### 2020-03-26 Common/chapters/transfer_learning.tex
Julien and Johan: minor

\subsection{Conclusion}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}This transfer learning approach using frozen and unfrozen parts allowed to increase the AUC of the model by 15\%. It increased the generalization ability of the model by learning features coming from different body parts. This makes the model more robust and more likely to classify new unseen data well. As this model reached an AUC ($0.80$) similar to the one a less-experienced radiologist can aim for ($0.81$), the goal of creating a model which generalizes well is reached. These improvements are a step forward in a field where the nonavailability of data is a real obstacle that prevents deep learning-based cancer classification systems from making a major breakthrough.

>>>>

\subsection{Conclusion}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}This transfer learning approach using frozen and unfrozen parts allowed to increase the AUC of the model by 18\%. It increased the generalization ability of the model by learning features coming from different body parts. This makes the model more robust and more likely to classify new unseen data well. As this model reached an AUC ($0.80$) similar to the one a less-experienced radiologist can aim for ($0.81$), the goal of creating a model which generalizes well is reached. These improvements are a step forward in a field where the nonavailability of data is a real obstacle that prevents deep learning-based cancer classification systems from making a major breakthrough.
